Assessment and optimization of respiratory syncytial virus prophylaxis regimens in Connecticut, \Sexpr{formatYear(startDate)}-\Sexpr{formatYear(endDate)}

### 2019-02-17 Paper/RSVOptimization.rnw
Moved todos
Ginny’s non-structural feedback
Qualify calls to knitr

<<options, echo=FALSE>>=
    opts_chunk$set(echo=FALSE, message=FALSE)
@

<<load>>=
read_chunk("../Analysis/RSV.R")
read_chunk("../Paper/RSVOptimization.R")
@

@@

\usepackage[hidelinks]{hyperref}
\usepackage[svgnames]{xcolor} % Must go before tikz and before structure.tex
\usepackage{tikz}
%\usepackage{draftwatermark}
%\SetWatermarkScale{1}
%\SetWatermarkAngle{45}
%\SetWatermarkFontSize{4ex}
%\SetWatermarkHorCenter{12ex}
%\SetWatermarkVerCenter{12ex}
%\SetWatermarkLightness{.5}
%\SetWatermarkText{DRAFT 5}

>>>>

<<options, echo=FALSE>>=
    knitr::opts_chunk$set(echo=FALSE, message=FALSE)
@

<<load>>=
knitr::read_chunk("../Analysis/RSV.R")
knitr::read_chunk("../Paper/RSVOptimization.R")
@

@@

\usepackage[hidelinks]{hyperref}
\usepackage[svgnames]{xcolor} % Must go before tikz and before structure.tex
\usepackage{tikz}
\usepackage{draftwatermark}
\SetWatermarkScale{1}
\SetWatermarkAngle{45}
\SetWatermarkFontSize{4ex}
\SetWatermarkHorCenter{12ex}
\SetWatermarkVerCenter{12ex}
\SetWatermarkLightness{.5}
\SetWatermarkText{DRAFT 1}
